%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Jordan}{Rodgers}{\href{mailto:com6056@gmail.com}{com6056@gmail.com} | 818.854.0342 | \href{https://linkedin.com/in/jrodgers2}{linkedin.com/in/jrodgers2} \\
\vspace{3pt} Searching for a Security/SRE/DevOps/InfraOps full-time position for Fall 2018
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Rochester Institute of}
\subsection{Technology}
\descript{BS in Networking and Systems Administration}
\descript{Minor in Computing Security}
\location{Expected May 2018 | Rochester, NY \\ GPA: 3.93}
\sectionsep
\vspace{-2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\location{Rochester Institute of Technology}
\vspace{0.3mm}
Dean's List (Fall '14 - Spring '17) \\
\vspace{1mm}
\location{Computer Science House}
\vspace{0.3mm}
SIH Floor Member of the Year ('15 - '16) \\
Member of the Year ('16 - '17)
\sectionsep
\vspace{-2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Links} 
%Github:// \href{https://github.com/deedydas}{\custombold{deedydas}} \\
%LinkedIn://  \href{https://www.linkedin.com/in/debarghyadas}{\custombold{debarghyadas}} \\
%YouTube://  \href{https://www.youtube.com/user/DeedyDash007}{\custombold{DeedyDash007}} \\
%Twitter://  \href{https://twitter.com/debarghya_das}{\custombold{@debarghya\_das}} \\
%Quora://  \href{https://www.quora.com/Debarghya-Das}{\custombold{Debarghya-Das}}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
% Computer Science I \\
Configuration Management \\
% Cryptography \& Authentication \\
Cyber Defense Techniques \\
% Databases and Data Modeling \\
% Fundamentals of Computing Security \\
Mobile Device Security \& Forensics \\
% Network Design and Performance \\
% Network Services \\
Network \& System Security Audit \\
% Python Scripting \\
% Routing and Switching \\
Storage Architectures \\
Systems Administration I \& II \\
% Virtualization \\
% Web \& Mobile I \\
Windows System Forensics
% Wireless Networking
\sectionsep
\vspace{-2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\location{Management \& Monitoring Tools:} 
Chef, Basic Puppet and Ansible, Terraform, VMware vSphere, oVirt, Proxmox, Zabbix, Datadog, Foreman \\
\vspace{5pt}
\location{Cloud Services/Providers:}
Amazon Web Services (EC2, RDS, VPC, S3, CloudFormation, Route 53, SQS, SNS and IAM), Google Cloud Platform (Compute Engine, IAM) \\
\vspace{5pt}
\location{Network \& Security:}
Cisco Switches \& Routers, HP Switches, Cisco \& Ruckus Wireless, Security Onion IDS, pfSense, Basic Metasploit, Various Security Tools \\
\vspace{5pt}
\location{Services \& Applications:}
Ceph, MySQL, PostgreSQL, Apache, FreeIPA, Active Directory, SCCM, Windows \& Linux DHCP \& DNS \\
\vspace{5pt}
\location{System Platforms:}
Linux (RHEL/Debian Based), Windows Server (2003-2016), macOS \\
\vspace{5pt}
\location{Development:}
Python, Android Java, Basic Ruby, Mock, Bash, Git
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Slack}
\descript{| Operations Engineering Intern}
\location{June 2017 – August 2017 | San Francisco, CA}
\vspace{-1mm}
\begin{itemize}
  \itemsep-4pt
  \item Expanded functionality of internal Python libraries and wrote unit tests.
  \item Improved efficiency of internal VM deprovisioning pipeline by over 85\%.
  \item Expanded internal VM provisioning pipeline to support Google Cloud Platform.
  \item Implemented a profiling system to time Chef runs.
  \item Worked with the QA team to upgrade and improve the QA environment.
  \item Implemented all necessary changes to upgrade internal and external systems to new OS and software versions and started the roll-out.
\end{itemize}
\vspace{-4.5mm}
\sectionsep

\runsubsection{Intuit}
\descript{| Security Engineering Intern}
\location{June 2016 – August 2016 | San Diego, CA}
\vspace{-3mm}
\begin{itemize}
  \itemsep-4pt
  \item Learned and used Chef to deploy JIRA and Alerta in AWS.
  \item Architected both to fit the needs of the rapidly-changing environment so they could be rebuilt from scratch at any time.
  \item Used multiple AWS services to securely deploy the applications.
  \item Tested multiple monitoring systems and implemented Datadog monitoring into the JIRA deployment.
  \item Learned the basics of Ruby to improve the automation of an internal system.
%   \item Did penetration testing on an outdated Java application and reported findings.
\end{itemize}
\vspace{-4.5mm}
\sectionsep

\runsubsection{Rochester Institute of Technology}
\descript{| Assistant Sysadmin}
\location{September 2014 – Present | Rochester, NY}
\vspace{-3mm}
\begin{itemize}
  \itemsep-4pt
  \item Working with the College of Engineering to support the various college systems including an oVirt virtual environment, Ceph cluster, and multiple RHEL and Windows Servers.
  \item Integrated oVirt with Ceph using Cinder and developed migration tooling.
%   \item Deployed initial implementation of Zabbix to assist in the monitoring of the college infrastructure.
%   \item Set up Rundeck to aid with the automation of Ansible and other tasks.
  \item Researched and implemented various other solutions to better serve the needs of the college.
\end{itemize}
\vspace{-5mm}
\sectionsep

\runsubsection{HighTech Los Angeles}
\descript{| Assistant Sysadmin}
\location{June 2011 – August 2015 | Van Nuys, CA}
% \vspace{-3mm}
% \begin{itemize}
%   \itemsep-4pt
%   \item Migrated to and implemented current email system, deployment system, printer server/accounting system, and web server.
%   \item Assisted in the upgrade to the current virtual environment, wireless infrastructure, and core networking.
%   \item Maintained multiple servers and completed multiple projects to improve infrastructure, strengthen security, and better serve the needs of the school.
%   \item Trained current IT Director and provide remote support when needed.
% \end{itemize}
\vspace{-1mm}
\sectionsep

\runsubsection{Unified Pictures}
\descript{| IT Assistant }
\location{June 2013 – August 2014 | Northridge, CA}
% \vspace{-3mm}
% \begin{itemize}
%   \itemsep-4pt
%   \item Upgraded and improved infrastructure and security for upcoming animated film.
%   \item Implemented multiple systems including the current wireless infrastructure, a render farm, and multiple NAS systems.
% \end{itemize}
% \vspace{-1mm}
\sectionsep

\vspace{-4mm}
\section{Activities/Projects}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACTIVITIES & INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vspace{-3mm}
% \section{Activities}
\runsubsection{Computer Science House}
\location{-\hspace{1.5mm}Chairman \href{https://csh.rit.edu/}{(csh.rit.edu)}}
\vspace{-3.5mm}
\begin{itemize}
  \itemsep-3pt
  \item Chairman serves as the head of the Computer Science House Executive Board, supervising the activities of the directors and acting as the primary spokesperson for Computer Science House.
  \item Previously served as the Operations and Communications Director.
  \item Currently a volunteer systems/network administrator and helps to maintain the various services running in the server room.
\end{itemize}
% \vspace{3pt}
% \runsubsection{Audio \& Video Production} \\
% \vspace{3pt}
% \runsubsection{Guitar}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-5.5mm}
% \section{Projects}

% \runsubsection{Ceph}
% \location{September 2016 – Present}
\location{\hspace{1mm}Ceph Project}
\vspace{-3mm}
\begin{itemize}
  \itemsep-4pt
  \item Built a Ceph storage cluster for the various storage needs of Computer Science House.
  \item Benchmarked and compared various different configurations and implementations to find the most optimal one possible with the resources available.
\end{itemize}
\vspace{-5.5mm}
\sectionsep

% \runsubsection{Firewall/IPS/IDS/Network Monitor}
% \location{October 2014 – Present}
\location{\hspace{1mm}Firewall/IPS/IDS/Network Monitor Project}
\vspace{-3mm}
\begin{itemize}
  \itemsep-4pt
  \item Researched and implemented a firewall (pfSense), IDS (Security Onion), and network monitor (ntopng) to monitor and block malicious traffic for Computer Science House infrastructure.
%   \item Using the firewall and IPS in conjunction with the IDS to further secure the network and aid in attack identification and prevention.
  \item Protects over 100 devices often utilizing close to gigabit throughput.
%   \item Requires constant monitoring and maintenance of rules in order to be effective.
%   \item Using alerts from the IDS to tune the IPS when necessary.
\end{itemize}
\vspace{-5mm}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
